Computing Entropies With Nested Sampling

### 2017-05-21 paper/ms.tex
A bit of clarification in the poisson process bit

When $N=1$, the sequence of $\ln X$ values is a Poisson process with rate
1. \citet{Walter2015} showed how this view of the NS sequence of points
can be used to construct a
version of NS that produces unbiased estimates of the evidence.
However, it can also be used to construct an unbiased estimator of
a log-probability, which is more relevant to information theoretic
quantities.

Given the definition of the NS algorithm,
the probability distribution for the proportion $t$ of the prior mass
retained on a given iteration is
\begin{align}
t_i &\sim \textnormal{Beta}(N, 1),
\end{align}
and the probability distribution for the sequence of $X$-values of
the discarded points is obtained from
\begin{align}
X_i &= \prod_{k=1}^i t_i.
\end{align}
The corresponding likelihood values of the discarded points are
denoted $L_1, L_2, L_3$, and so on.

Consider a particular likelihood value $\ell$ whose $X$-value
we would like to know.
The number of discarded points with likelihood below $\ell$, i.e.,
the number of NS iterations taken reach a likelihood above
$\ell$, is
\begin{align}
n(L_i < \ell) &= \sum_i \mathds{1}\left(L_i < \ell\right) \\
              &= \sum_i \mathds{1}\left(X_i > X(\ell)\right)
\end{align}
The expected value of $n$ given the definition of the algorithm is
\begin{align}
\left<n(L_i < \ell)\right> &= 
              \sum_i \left<\mathds{1}\left(X_i > X(\ell)\right)\right>
\end{align}

>>>>

The sequence of $\ln X$ values produced by a Nested Sampling run can be
considered as a Poisson process with rate equal to $N$, the number of
particles. For example, when $N=1$, the distribution for $\ln X_{i+1}$
given $\ln X_i$ is a shifted (and reflected) exponential with rate 1.
\citet{Walter2015} showed how this view of the NS sequence of points
can be used to construct a
version of NS that produces unbiased (in the frequentist sense)
estimates of the evidence.
However, it can also be used to construct an unbiased estimator of
a log-probability, which is more relevant to information theoretic
quantities.

Consider a particular likelihood value $\ell$ whose corresponding $X$-value
we would like to know. Since the $\ln X_i$ values have the same distribution
as the arrival times of a Poisson process with rate $N$, the probability
distribution for the number of points in an interval of length $t$ is
Poisson with expected value $\lambda t$. Therefore the expected number of
NS discarded points with likelihood below $\ell$ is $-\ln X(\ell)$:
\begin{align}
\big< n(L(\x_i) \leq \ell) \big> &= -\ln X(\ell).
\end{align}
We can therefore take $n(L(\x_i) \leq \ell)$, the number of points in the
sequence with likelihood below $\ell$, as an unbiased estimator of
$-\ln X(\ell)$.
